---
title: "Text Mining"
author: "Parnian Jahangiri Rad"
date: "3/19/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing Dickens books  
We will use these libraries:  
```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(gutenbergr)
library(tidytext)
library(wordcloud2)
library(ragg)
library(graphics)
```

We will download all his novels using `gutenbergr` package.  
  
#### Find 20 most common words in Dickens novels  
  
After removing stop words, we will find 20 words that Dickens used most
in his novels:  
```{r}
x <- gutenberg_works(author == "Dickens, Charles")

books <- c("The Pickwick Papers",
           "Oliver Twist",
           "Nicholas Nickleby",
           "The Old Curiosity Shop",
           "Barnaby Rudge: A Tale of the Riots of 'Eighty",
           "Martin Chuzzlewit", 
           "Dombey and Son", 
           "David Copperfield", 
           "Bleak House",
           "Hard Times", 
           "Little Dorrit", 
           "A Tale of Two Cities", 
           "Great Expectations", 
           "Our Mutual Friend", 
           "The Mystery of Edwin Drood") 

ids <- array(dim = length(books))
count <- 1 
for (i in books){
  ids[count] <- x[x$title==i,"gutenberg_id"]$gutenberg_id
  count <- count + 1
}

dickens <- gutenberg_download(ids,mirror =  "http://mirrors.xmission.com/gutenberg/")

tidy_dickens <- dickens %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

td <- tidy_dickens %>%
  count(word, sort = TRUE) %>%
  mutate(word = reorder(word, n))
```

```{r}
td_20 <- td %>% top_n(20)

ggplot(td_20,aes(x=n,y=word)) + 
  geom_bar(stat = "identity",fill="blueviolet") +
  ggtitle("top 20 words Dickens used most")
```
  
    
#### Wordcloud of 200 most common words in Dickens novels  
Now, we want to draw the wordcloud of 200 words that Dickens used most:  
```{r}
td %>%
  arrange(desc(n)) %>%
  head(200) %>%
  wordcloud2(size = 1,
    shape = "circle",color = "random-dark",
    minRotation = pi/2, maxRotation = -pi/2, minSize = 10,
    rotateRatio = 1)
```
  
#### Main characters of Dickens novels  
In order to find the most important characters in the novels, first we will find the words with capital letters as their first letter.
Then we will check if there is any mentions of that word while its first letter is lower case as well.If there is not, the word can be considered as a name.  
```{r}
names <- dickens %>%
  unnest_tokens(word, text, to_lower = F) %>%
  mutate(word = str_extract(word, "[A-Z][a-z]+")) %>%
  na.omit()

words <- dickens %>%
  unnest_tokens(word, text, to_lower = F) %>%
  mutate(word = str_extract(word, "[a-z]+")) %>%
  na.omit()


names <- names[!str_to_lower(names$word) %in% words$word,]


names <- names %>% 
  group_by(gutenberg_id) %>% 
  filter((word!="Mr") & (word!="Mrs")) %>% 
  count(word)

book_ids <- data.frame(ids, books)

characters <- tibble(names) %>%
  group_by(gutenberg_id) %>% 
  mutate() %>% 
  top_n(5) 
for (id in book_ids$ids){
  characters[characters$gutenberg_id==id, "Book"] <- book_ids[book_ids$ids==id, "books"]
}
```

```{r}
characters <- characters %>%
  group_by(Book)
p <- ggplot(data = characters,
       aes(x = reorder(word,n) ,
           y = n ,
           fill = Book)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(.~Book, scales = 'free') +
  labs(x = NULL,y = NULL) +
  theme(axis.text.x = element_blank())
```

```{r}
pngfile <- fs::path(knitr::fig_path(),  "scaling.png")
agg_png(pngfile, width = 60, height = 36, units = "cm", res = 300, scaling = 2)
plot(p)
invisible(dev.off())
knitr::include_graphics(pngfile)
```
  
#### Find 10 most common verbs done by men and women  
```{r}
dickens_4gram<- dickens %>% 
  unnest_tokens(bigram, text, token = "ngrams", n = 4)
dickens_4gram_heshe <- dickens_4gram %>% 
  separate(bigram, c("word1","word2","word3","word4"), sep=" ") %>% 
  filter(word1=="he" | word1=="she") %>% 
  filter(word2!="is" | (word2=="is" & (word3!="not" & word3!="a" & word3!="an") )) %>% 
  filter(word2!="was" | (word2=="was" & (word3!="not" & word3!="a" & word3!="an") ))
dickens_4gram_heshe_backup <- dickens_4gram_heshe

aux <- tribble(~word,"had","have","has","was","is","would","could","did","might","should")
aux2 <- tribble(~word,"been","never")
dickens_4gram_heshe <- dickens_4gram_heshe_backup
dickens_4gram_heshe %>% 
  mutate(second_word = ifelse(
    !(dickens_4gram_heshe$word2%in%aux$word),
     dickens_4gram_heshe$word2,ifelse(
        !(dickens_4gram_heshe$word3%in%aux2$word),
        dickens_4gram_heshe$word3,dickens_4gram_heshe$word4)))->dickens_4gram_heshe2
dickens_4gram_heshe2 %>% 
  filter(second_word!="not"&second_word!="have"&second_word!="and"&second_word!="so") %>% 
  filter(second_word!="a" & second_word!="an"&second_word!="will"&second_word!="be",) %>%
  filter(second_word!="the"&second_word!="were",second_word!="in") %>% 
  group_by(word1,second_word) %>% 
  summarise(count=n()) %>% 
  ungroup() %>% 
  group_by(word1) %>% 
  arrange(desc(count)) %>% 
  slice(1:10) %>% 
  mutate(top=seq_along(word1))->dickens_4gram_heshe3


ggplot(dickens_4gram_heshe3,aes(x=-top,y=count,fill=word1))+
  geom_bar(stat = "identity")+
  facet_wrap(. ~ word1)+
  geom_text(aes(y = count+50, label = second_word), hjust = "left")+
  coord_flip()+
  labs(x=NULL)+
  scale_y_continuous(limits = c(0,max(dickens_4gram_heshe3$count)*1.1))+
  theme_minimal()+
  theme(legend.position = 'none',
        axis.text.y = element_blank())
```
  
#### Bigrams of `The Pickwick Papers` and `Oliver Twist`  

```{r}
x <- gutenberg_works(author == "Dickens, Charles")

books <- c("The Pickwick Papers",
           "Oliver Twist") 

ids <- array(dim = length(books))
cnt <- 1 
for (i in books){
  ids[cnt] <- x[x$title==i,"gutenberg_id"]$gutenberg_id
  cnt <- cnt + 1
}

Books <- gutenberg_download(ids, meta_fields = "title",mirror = "http://mirrors.xmission.com/gutenberg/")

books <- Books %>%
  group_by(title) %>%
  mutate(line = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

pick <- books[(books$title=="The Pickwick Papers") & (books$chapter >= 58), ]
pick$chapter <- pick$chapter - 57 

oliver <- books[(books$title=="Oliver Twist") & (books$chapter >= 1), ]
```

```{r}
pick_bigrams <- pick %>% group_by(chapter)  %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% na.omit() %>%
  count(bigram, sort = TRUE)

oliver_bigrams <- oliver %>% group_by(chapter)  %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% na.omit() %>%
  count(bigram, sort = TRUE)
```

```{r}
pick_bigrams <- pick_bigrams %>%
  group_by(chapter) %>%
  top_n(3)

pick_bi <- ggplot(pick_bigrams,aes(x = bigram, y = n, fill = chapter)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(.~ chapter, scales = 'free') +
  labs(x = NULL,y = NULL) +
  theme(axis.text.x = element_blank())
```

```{r}
pngfile <- fs::path(knitr::fig_path(),  "scaling.png")
agg_png(pngfile, width = 60, height = 36, units = "cm", res = 300, scaling = 2)
plot(pick_bi)
invisible(dev.off())
knitr::include_graphics(pngfile)
```

```{r}
oliver_bigrams <- oliver_bigrams %>%
  group_by(chapter) %>%
  top_n(3)

Oliver_bi <- ggplot(oliver_bigrams,aes(x = bigram, y = n, fill = chapter)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  facet_wrap(.~ chapter, scales = 'free') +
  labs(x = NULL,y = NULL) +
  theme(axis.text.x = element_blank())
```

```{r}
pngfile <- fs::path(knitr::fig_path(),  "scaling.png")
agg_png(pngfile, width = 60, height = 36, units = "cm", res = 300, scaling = 2)
plot(pick_bi)
invisible(dev.off())
knitr::include_graphics(pngfile)
```
  
#### Compare unigrams of all dickens books  

```{r}
x <- gutenberg_works(author == "Dickens, Charles")

books <- c("The Pickwick Papers",
           "Oliver Twist",
           "Nicholas Nickleby",
           "The Old Curiosity Shop",
           "Barnaby Rudge: A Tale of the Riots of 'Eighty",
           "Martin Chuzzlewit", 
           "Dombey and Son", 
           "David Copperfield", 
           "Bleak House",
           "Hard Times", 
           "Little Dorrit", 
           "A Tale of Two Cities", 
           "Great Expectations", 
           "Our Mutual Friend", 
           "The Mystery of Edwin Drood") 

ids <- array(dim = length(books))
count <- 1 
for (i in books){
  ids[count] <- x[x$title==i,"gutenberg_id"]$gutenberg_id
  count <- count + 1
}

dickens_books <- gutenberg_download(ids, meta_fields = "title",
                    mirror = "http://mirrors.xmission.com/gutenberg/")
```

```{r,warning=FALSE,message=FALSE}
dickens_unigrams <- dickens_books %>%
  unnest_tokens(one_gram, text, token = "ngrams", n = 1) %>% 
  filter(!one_gram %in% stop_words$word) %>% 
  group_by(title,one_gram) %>% 
  summarise(freq = n()) %>% 
  ungroup() %>% 
  group_by(title) %>% 
  arrange(desc(freq)) %>% 
  mutate(rank = seq_along(one_gram))

ggplot(dickens_unigrams,aes(x=log10(rank) , y=log10(freq)))+
  geom_line(aes(group=title , color=title), size=1)
```

### Sentiment Analysis of `Les Miserables`    
We are going to clean the text of Les Miserables and then, rank the sentiment of each word. At the end, we  will divide this book into 200 parts and cont the number of positive and negative words in each part.  
We will see that Les miserables is a sad story.  
```{r}
daat <- gutenberg_metadata %>% filter(title == "Les Misérables")
book <- gutenberg_download(daat$gutenberg_id,
                mirror="http://mirrors.xmission.com/gutenberg/")
words <- book %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

words <- words %>%
  dplyr::mutate(order = row_number()) %>%  
  inner_join(get_sentiments("bing"))

emotion <- words %>%
  mutate(index = floor(words$order/(last(words$order)/200))) %>%
  group_by(index ,sentiment) %>%
  dplyr::count() %>%
  tidyr::spread(sentiment, n, fill = 0)  

emotion <- emotion[1:nrow(emotion)-1,]
```

```{r}
ggplot() + 
  geom_line(data=emotion, aes(x=index, y = positive, color = "steelblue"), size=1) + 
  geom_line(data=emotion, aes(x=index, y = negative, color="darkred"), size=1) +
  ylab('Sentiment') + xlab('Part')+
  scale_color_discrete(labels = c("negative Sentiment", "positive Sentiment"))
```
